---
title: "Trends & Correlations"
output: html_document
---

```{r setup, echo=FALSE}
library(ggplot2)
library(gtrendsR)
library(corrplot)
library(ggpubr)
Projdata <- read.csv("~/Downloads/Project Data - Sheet1.csv")
TSdata <- ts(Projdata,frequency = 12,start=c(2004,1))
BSTrend <- gtrends(c("Behavioral Science"),time="all")
BSTrend <- ts(BSTrend$interest_over_time$hits,frequency = 12,start=c(2004,1))
BSSeason <- gtrends(c("Behavioral Science"),time="2004-1-01 2009-12-31")
BSSeason <- ts(BSSeason$interest_over_time$hits,frequency = 12,start=c(2004,1))
```

###Trends

**Decomposition of Behavioral Science**

```{r decomp, echo=FALSE}
decompBS <- decompose(BSTrend)
plot(decompBS)
plot(unique(decompBS$seasonal),type="l", main="Seasonality Trend",ylab="Effect on Search",xlab="Month")
```

**General Trends**

*Behavioral vs Behavioural Science*

```{r worldtrends, echo=FALSE}
worldtrend<-gtrends(c("Behavioral Science","Behavioural Science"),time="all")
plot(worldtrend)
```

*Behavioral Science in America, Great Britain, and Canada*

```{r countrytrends, echo=FALSE}
countrytrend<-gtrends(c("Behavioral Science"),geo=c("US","GB","CA"),time="all")
plot(countrytrend)
```

*Behavioral vs Behavioural Insights*

```{r insightstrends, echo=FALSE}
diworldtrend<-gtrends(c("Behavioral Insights","Behavioural Insights"),time="all")
plot(diworldtrend)
```

*Behavioral Insights in America, Great Britain, and Canada*

```{r cinsightstrends, echo=FALSE}
dicountrytrend<-gtrends(c("Behavioural Insights"),geo=c("US","GB","CA"),time="all")
plot(dicountrytrend)
```

*Data vs Behavior*

```{r datatrends, echo=FALSE}
dsworldtrend<-gtrends(c("Data Science","Data Scientist","Behavioral Scientist"," Behavioral Science"),time="all")
plot(dsworldtrend)
```

*Data Science in America, Great Britain, and Canada*

```{r worlddatatrends, echo=FALSE}
dscountrytrend<-gtrends(c("Data Science"),geo=c("US","GB","CA"),time="all")
plot(dscountrytrend)
```

*All Term Trends*

```{r termtrends, echo=FALSE}
plot(TSdata, main = "Trends For All Search Terms",las=1,cex.lab=0.5)
```

###Correlations

*Numbers Then Visualization*

```{r correlations, echo=FALSE}
cormat<-cor(Projdata)
corrplot(cormat,method='circle')
```

**Points of interest**
 
 * Behavioural Insights (more than behavioral insights) correlation with data science (and data scientist)
 * Data science (and data scientist) & bias are pretty strongly correlated
 * Behavioral Science has some negative correlation with Nudge

```{r correlationplots, echo=FALSE}
ggscatter(Projdata,x="data.science",y="Behavioural.Insights", add="reg.line",cor.coef = TRUE, main="Correlation of Data Science & Behavioural Insights", ylab="Behavioural Insights",xlab="Data Science")


ggscatter(Projdata,x="data.science",y="Bias", add="reg.line",cor.coef = TRUE, main="Correlation of Data Science & Bias", xlab="Data Science")


ggscatter(Projdata,x="Behavioral.Science",y="Nudge", add="reg.line",cor.coef = TRUE, main="Correlation of Behavioral Science & Nudge",xlab="Behavioral Science")
```
